---
title: "Assignment7_A"
author: "33140 (Sahil Naphade)"
date: "22/04/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

 Roll no. 33140
 Batch: L9
 Assignment 7: Generate wordcloud (1)

1. Install and load libraries
```{r}

setwd("G:/College/SL6/Assignment7/")
# Install
#install.packages("tm")  # for text mining
#install.packages("SnowballC") # for text stemming
#install.packages("wordcloud") # word-cloud generator 
#install.packages("RColorBrewer") # color palettes
#install.packages("wordcloud2") # word-cloud generator 
#install.packages('readtext')
# Load
library("tm")
library("SnowballC")
library("wordcloud")
library("RColorBrewer")
library("wordcloud2")
library("readtext")

```

2. Read the text file, load as Corpus and inspect the file
```{r}
#load the text

text <- readtext("../../Sl-VI DataSets/TextMining/NarendraModi.txt")

#Load the data as a corpus
docs <- Corpus(VectorSource(text))

#Inspect part of the content of the document
inspect(docs)
```

3. Preparation of data
  a. Remove White spaces from data
```{r}
  # remove white spaces  
text_data <- tm_map(docs,stripWhitespace)
  inspect(text_data)
  
```
  
  b. Convert all the words to lower alphabets
```{r}
  # convert to lower
  text_data <- tm_map(text_data,tolower)
  inspect(text_data)
```
  
  c. Remove the numbers
```{r}
# Remove numbers
  text_data <- tm_map(text_data,removeNumbers)
  inspect(text_data)
  
```
  
  d. Remove punctuations in the text
```{r}
# Remove punctuations
  text_data <- tm_map(text_data,removePunctuation)
  inspect(text_data)
```
  
  e. Remove stop-words
```{r}
# Remove stop-words
  text_data <- tm_map(text_data,removeWords,stopwords('english'))
  inspect(text_data)
```
  
4. Load the data into Term Document Matrix, convert in a matrix, sort the data as increasing number of occurances, load as a dataframe
```{r}
  # Create a TDM
dtm <- TermDocumentMatrix(text_data) 
matrix <- as.matrix(dtm) 
words <- sort(rowSums(matrix),decreasing=TRUE) 
df <- data.frame(word = names(words),freq=words)
str(df)
```

5. Generate Word Cloud
```{r}
set.seed(1234) # for reproducibility 
wordcloud(words = df$word, freq = df$freq, min.freq = 1,max.words=15, random.order=FALSE,rot.per=0.35,colors=brewer.pal(8, "Dark2"))

```

